A Hybrid Neutronics Method for Time-Dependent Control Rod Modeling in Molten Salt Reactors

### 2024-11-07 transient.tex
Rod drop content

Section \ref{sec:rod-drop}

@@

>>>>

Section \ref{sec:rod-drop} covers the model setup, numerical results, and discussion of the rod
drop experiment. Section \ref{sec:reactivity-insertion} covers the model setup, numerical results,
and discussion of the reactivity insertion experiment. Lastly, Section \ref{sec:transient-summary}
summarizes the goals and outcomes in this chapter.

@@

\gls{MSRE} researchers conducted a series of rod drop experiments at three different $^{235}$U
loadings \cite{prince_zero-power_1968}. These experimented were conducted from an initially critical
and low power state with an initial neutron count rate of approximately 30,000 from neutron detectors
placed near the reactor. A rapid-action camera photographed the integral count shown on the
detectors about once every second starting from a few seconds before the rod drop to about thirty
seconds after the rod drop. This work aims to replicate the integral count curve following a rod
drop of Rod 1 with the $^{235}$U loading corresponding to "30 capsule additions" of highly-enriched
$^{235}$U capsules.
